Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-21 analysis/paper/paper.Rmd
Update paper.Rmd

In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications (See appendix for details on the methodology).

>>>>

In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications (see appendix for details on the methodology).
